The Chemistry Development Kit (CDK). 3. Atom typing, Rendering, Molecular Formula, and Substructure Searching

### 2015-12-23 article.tex
A bit more content

@@

@@

@@

  PMD ...

@@

@@

INVITE NINA

@@

Over the past years since the last CDK publication in 2006, a lot has changed. The functionality
has seen many additions, and the stability of the development model has significantly improved.
This paper outlines how peer review and quality control contributed to a much wider adoption
of our cheminformatics library and seen many new additions. With over 75 contributors,
the CDK is alive and kicking.

>>>>

  New classes include:

@@

  \subsubsection*{Structure Diagram Layout}

  The structure diagram layout ... %FIXME: John, do you want this in?

@@

% FIXME: add dependency plot

@@

The project continues to use PMD (http://pmd.sf.net/) for code quality checking,
but deviates from the default rules. For example, we are more liberal with 
variable name length. Moreover, a number of additional PMD tests have been
developed specifically for the CDK, that, for example, test if a class uses
the core interfaces instead of implementations of those interfaces. For example,
that the code uses IAtom instead of Atom. That said, these tests do generate a
few false positives, as the tests check the class name only, and not the
Java package the class is in.

@@

Another change made over the past years is the move to a Git-based version
control system. Advantages the projects makes advantage of is the distributed
nature of Git repositories, and easier branching and making available of
patches. GitHub has replaced SourceForge as the main source code hosting service
where we can use novel approaches for commenting on code, pull requests, etc.
These new features simplify our code review process.

@@

Another recent change is the choice of build system: we have moved away from
Ant to Maven to deal with dependencies and compile the library.

% FIXME: write more about this, and provide info about Maven Central

@@

Over the past years since the last CDK publication in 2006, a lot has changed. The functionality
has seen many additions, and the stability of the development model has significantly improved.
This paper outlines how peer review and quality control contributed to a much wider adoption
of our cheminformatics library and seen many new additions. With 93 contributors,
the CDK is alive and kicking.
